**Measuring Depression and Anxiety with 4 items? Adaptation of the PHQ-4 to increase its Sensitivity to Subclinical Variability**

### 2024-12-12 paper/4_WIP/manuscript.qmd
updated manuscript

    documentmode: jou

@@

The final sample included 836 participants (Mean age = 25.1 +- 11.3 [18, 76]; 73.8\% women).
This study was approved by the University of Sussex' Ethics Committee **(ER/...)**.

@@

The STAI-5 [@zsido2020development] was used as a ground truth measure of anxiety. This abridged version of the STAI (**TODO: add ref**) includes 5 items rated on a 4-point Likert scale. Changes were made in the instructions from asking *"how participants feel right now"* to *"over the past 2 weeks"* to keep it consistent with the instructions of the PHQ-4 and BDI-II. A general score of anxiety was computed by averaging all the items.

@@

The linear regression predicting the BDI-II total score with the PHQ-4 depression score showed no interaction related to the PHQ-4 version ($\Delta Intercept_{\text{refined}} = TODO; \Delta \beta_{\text{refined}} = TODO$), suggesting no differences in the relationship pattern between the two versions (see @fig-two).

Moreover, Bayesian *t*-tests (using *BayesFactor*'s `ttestBF()` function with default priors; **ADD REF TO PKG**) comparing the BDI-II scores between the refined and the original version at each integer score (0, 1, 2, 3) yielded no evidence in favour of a significant difference (BF > 3). In other words, having the same score on the refined version as on the original version was related to the same outcome on the BDI-II.

@@

The linear regression predicting the STAI-5 general score with the PHQ-4 anxiety score showed no interaction related to the PHQ-4 version ($\Delta Intercept_{\text{refined}} = TODO; \Delta \beta_{\text{refined}} = TODO$), suggesting no differences in the relationship pattern between the two versions.

>>>>

    documentmode: man
editor: 
  markdown: 
    wrap: 72

@@

The final sample included 836 participants (Mean age = 25.1 +- 11.3 [18, 76]; 73.8\% women).
This study was approved by the University of Sussex' Ethics Committee (ER/ASF25/4).

@@

The STAI-T5 [@zsido2020development] was used as a ground truth measure of anxiety. This abridged version of the STAI [@marteau1992development] includes 5 items rated on a 4-point Likert scale. Changes were made in the instructions from asking *"how participants feel right now"* to *"over the past 2 weeks"* to keep it consistent with the instructions of the PHQ-4 and BDI-II. A general score of anxiety was computed by averaging all the items.

@@

The linear regression predicting the BDI-II total score with the PHQ-4 depression score showed no interaction related to the PHQ-4 version ($\Delta Intercept_{\text{refined}} =  -0.13, 95\% CI[-1.73, 1.47], t(832) =  -0.16, p = 0.871 ; \Delta \beta_{\text{refined}} = -0.05, 95\% CI[-0.70, 0.60], t(832) = -0.15 , p = 0.883$), suggesting no differences in the relationship pattern between the two versions (see @fig-two).

Moreover, Bayesian *t*-tests (using *BayesFactor*'s `ttestBF()` function with default priors; @moreyrouder2024) comparing the BDI-II scores between the refined and the original version at each integer score (0, 1, 2, 3) yielded no evidence in favour of a significant difference (BF > 3). In other words, having the same score on the refined version as on the original version was related to the same outcome on the BDI-II.

@@

The linear regression predicting the STAI-5 general score with the PHQ-4 anxiety score showed no interaction related to the PHQ-4 version ($\Delta Intercept_{\text{refined}} =  -0.02, 95\% CI[-0.15, 0.11], t(832) =  -0.32, p = 0.750; \Delta \beta_{\text{refined}} = 0.01, 95\% CI[-0.03, 0.05], t(832) = 0.56 , p = 0.576$), suggesting no differences in the relationship pattern between the two versions.
